---
title: "General Social Survey"
author: "Estrella Aguilar"
date: "Year 2024"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(foreign)
source("GrabData.R")
```






#  Question 2

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Is there a difference in years of education (EDUC) between the those who did or did not vote in 2016 (VOTE16)? 

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I looked at the data and it had a numerical variable which was education and had a factor variable which was VOTE16 so I used the Numerical~cat/rmd helper file!



##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

### Descriptive Results

#### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(EDUC~VOTE16,data=GSSdata)
```

 I'm looking at the median, people who voted have a median of 15 years of education and people who did not vote have a median of 13 years of education.



#### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(EDUC~VOTE16,data=GSSdata)
```

Looking at the numerical results we can see that people who voted have a higher average education level of 15.625 years and those who did not vote have a lower average education level at 13.7 years. 128 people voted and 50 people did not vote which shows that people who have a higher level of education tend to vote more. 


### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(EDUC~VOTE16,data=GSSdata)
```

The inferential results give us low p value which is the statistical evidence between the education level of people who voted and the people who didn't vote, we can see the mean education level in the group that voted is 15.625 and the mean education level in the group of people who did not vote is 13.680. 

### Discussion and Conclusion

In conclusion people who have a higher education vote more and people who have a lower education vote less with people who voted having a mean education level of 15 and people who did not vote having a mean education level of 13.

